---
title: "National Park Service Acoustic Dataset"
author: "Rachel Ramirez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{National Park Service Acoustic Dataset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
# library(ggplot2)
library(NPS)


 data('dataSource')
dataSource <- as.data.frame(dataSource)

 data('cleandata')
 cleandata <- as.data.frame(cleandata)
```

The goal of the NPS package is to allow a user to explore the original NPS geospatial data and the cleaned NPS data according to assumptions/imputations made.  

## NPS Inputs

One can use the different inputs available on the sidebar of the shiny app to explore the data. The descriptions of most of the geospatial data are available from the NPS Report "Explanatory Variable Generation for Geospatial Sound Modeling" available here: http://irma.nps.gov/App/Reference/Welcome and the Natural Resource Publications Management website (http://www.nature.nps.gov/publications/nrpm/) search for `Explanatory variable generation for geospatial soundscape modeling: Standard operating procedure. Natural Resource Report. Natural Resource Report NPS/NRSS/NRR—2015/936` by Lisa Nelson, Michelle Kinseth, and Thomas Flowe.


## Figures

Here are two plots side by side of the original versus "cleaned" data using imputation techniques layed out in thesis. 

```{r, fig.show='hold', fig.cap = "Original versus Cleaned Data"}
 
# ggplot(dataSource, aes(x= (park), y = Wind_CRU)) +
#  geom_point() + coord_flip()
# 
# ggplot(cleandata, aes(x= park, y = Wind_CRU)) + 
#   geom_point() + coord_flip()
```
 

 
 
 